Football Championship Ticket Options

### 2018-09-07 paper.Rmd
Data reconcile and updates

```{r}
library(dplyr)

optionsDatNew = readr::read_csv("optionsDatNew.csv")

test = optionsDatNew %>% 
  select(name, dateTime, contains("price"))

library(ggplot2)

alabamaTS = test %>% 
  filter(name == "Alabama") %>% 
  select(dateTime, LL_price) %>% 
  mutate(dateTime = lubridate::ymd_hms(dateTime), 
         dateTime = lubridate::day(dateTime)) %>% 
  ts(.)

library(forecast)

alabamaForecast = HoltWinters(alabamaTS, beta = FALSE, gamma = FALSE)

@@

@@

initialData = initialData %>% 
  left_join(., previousYearRank, by = c("name" = "Team")) %>% 
  group_by(name)

initialData %>% 
  slice(., 1L) %>% 
  filter(masseyYearEnd < 50) %>% 
  ggplot(., aes(masseyYearEnd, as.numeric(LL_price))) +
  geom_point()

>>>>

@@

As a starting point, we began by looking at Massey's year-end rankings and early option prices (February 2018).

In an effort to reduce visual clutter and focus on potentially high-value teams, we can visually inspect the top 25 teams at the end of the 2017-2018 season.

@@

previousYearRank = previousYearRank %>% 
  mutate(Team = as.character(Team), 
         Team = gsub("St$", "State", Team))

initialData = initialData %>% 
  mutate(name = gsub("\\.|,", "", name)) %>% 
  left_join(., previousYearRank, by = c("name" = "Team")) %>% 
  group_by(name)

initialData %>% 
  slice(., 1L) %>% 
  filter(masseyYearEnd < 25) %>% 
  ggplot(., aes(masseyYearEnd, as.numeric(LL_price), color = as.factor(masseyYearEnd))) +
  geom_point() +
  theme_minimal()
```

Visually, there is cer

### Prices By Conference

```{r}
